---
title: "The Air Quality Dataset"
author: "Luke Morison"
date: "23/08/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Summary of Air Quality Dataset


>This exercise will be working with the built-in air quality dataset.^[ Chambers, J. M., Cleveland, W. S., Kleiner, B. and Tukey, P. A. _(1983)_ Graphical Methods for Data Analysis. Belmont, CA: Wadsworth.] This dataset contains 154 daily air quality measurements in New York from May 1, 1973 _(a Tuesday)_ to September 30, 1973. The dataset contains 6 variables

-  **Ozone**: Mean ozone in parts per billion _(ppb)_ from 1300 to 1500 hours at Roosevelt Island;
-  **Solar.R**: Solar radiation in Langleys _(lang)_ in the frequency band 4000–7700 Angstroms from 0800 to 1200 hours at Central Park;
-  **Wind**: Average wind speed in miles per hour _(mph)_ at 0700 and 1000 hours at LaGuardia Airport;
-  **Temp**: Maximum daily temperature in degrees Fahrenheit _(oF)_ at LaGuardia Airport;
-  **Month**: numeric month _(1-12)_
-  **Day**: numeric Day of the month _(1-31)_

### Table of Top of the Air Quality Dataset
```{r, echo=FALSE}
knitr::kable(head(airquality), caption = "Top of the Air Quality Dataset")
```

###Plot of Ozone by Temperature - Air Quality Dataset
```{r, echo=FALSE}
plot(airquality$Temp, airquality$Ozone,  
        main="Airquality: Ozone by Temperature") 

```


